---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# RealEstateR
[![Travis build status](https://travis-ci.org/estebanangelm/RealEstateR.svg?branch=master)](https://travis-ci.org/estebanangelm/RealEstateR)[![Coverage status](https://coveralls.io/repos/github/estebanangelm/RealEstateR/badge.svg)](https://coveralls.io/r/estebanangelm/RealEstateR?branch=master)[![Coverage status](https://codecov.io/gh/estebanangelm/RealEstateR/branch/master/graph/badge.svg)](https://codecov.io/github/estebanangelm/RealEstateR?branch=master)

Set of R tools for analyzing real estate data from Zillow and other sources.

## Installation

You can install the released version of RealEstateR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("RealEstateR")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("estebanangelm/RealEstateR")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

## Contribution

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
